Approximate State Abstraction

### 2016-01-30 paper/paper.tex
First pass at setting up the homogenized MDP description for lemma 2

% --- Notation Commands ---
\newcommand{\ep}{\widetilde \phi}
\newcommand{\epQ}{\ep_{Q^*}}
\newcommand{\epM}{\ep_{\text{model}}}
\newcommand\defn[1]{{\bf Definition:} #1}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\textbf{Proof:}
We begin by showing that Q values in the abstract \ac{MDP} closely resemble those in the ground \ac{MDP}.

@@

{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{model}$ type:
\begin{equation}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}{(1-\gamma)^3}
\end{equation}

{\bf Proof:}
Given the ground \ac{MDP}, $M_G$, consider the \ac{MDP}, $M_G'$ which is identical to $M_G$ except in its transition and rewards.

\begin{equation}
M_G' =  \langle \mathcal{S}_G, \mathcal{A}, \mathcal{R}_G', \mathcal{T}_G', \gamma \rangle
\end{equation}

Where
\begin{align}
\mathcal{R}_G'(s,a) = R_A(\epM(s), a)\\
\mathcal{T}_G'(s,a, s') = R_A(\epM(s), a, \epM(s'))
\end{align}

We know by \cite{li2006towards} that .

>>>>

% --- Notation Commands ---
\newcommand{\ep}{\widetilde \phi}
\newcommand{\epQ}{\ep_{Q^*}}
\newcommand{\epM}{\ep_{\text{model}}}
\newcommand\defn[1]{{\bf Definition:} #1}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\mcS}{\mathcal{S}}
\newcommand{\mcT}{\mathcal{T}}
\newcommand{\mcR}{\mathcal{R}}
\newcommand{\pM}{\phi_{\text{model}}}

@@

\textbf{Proof:}

@@

{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{model}$ type:
\begin{equation}
\label{eq:lemma2}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}{(1-\gamma)^3}
\end{equation}

{\bf Proof:} Our proof proceeds as follows: converting a ground \ac{MDP}, $M_G$, to an abstract \ac{MDP}, $M_A$, using a fixed but arbitrary aggregation function, $\ep_m$, that satisfies the $\epM$ criteria is shown to be equivalent to creating an intermediate \ac{MDP}, ${M_G}'$ and then applying an aggregation of the $\pM$ type. ${M_G}'$ is shown to have Q values identical to $M_A$ and Q values boundedly close to $M_G$ -- applying Lemma 1 we are able to conclude Lemma 2.

\enote{Maybe introduce language of ``homogenization"}

\begin{equation}
{M_G}' =  \langle \mathcal{S}_G, \mathcal{A}, \mathcal{R}_G', \mathcal{T}_G', \gamma \rangle
\end{equation}

Where
\begin{align}
{\mcR_G}'(s,a) = \mcR_A(\ep_m(s), a)\\
{\mcT_G}'(s,a, s') = \frac{\mcT_A(\ep_m(s), a, \ep_m(s'))}{|X(s')|}
\end{align}

where $X(s') = \{g \in \mathcal{S}_G | \ep_m(g) = \ep_m(s')\}$.

It is easily verifiable that ${\mcT_G}'$ induces a valid probability distribution.

Next note that the rewards of states in ${M_G}'$ that are aggregated in $M_A$ are identical:
\begin{align*}
&\forall{s1_G, s2_G \in \mc{S}_G, a} \\
&\left[ \epM(s1_G) = \epM(s2_G) \rightarrow {\mcR_G}'(s1_G, a) = {\mcR_G}'(s2_G, a) \right]
\end{align*}

Similarly, the transitions of states in ${M_G}'$ that are aggregated in $M_A$ are identical:
\begin{align*}
\forall{s1_G, s2_G, {s_G}' \in \mcS_G, a}\\
\left[ \epM(s1_G) = \epM(s2_G) \rightarrow {\mcT_G}'(s1_G, a, {s_G}') = {\mcT_G}'(s2_G, a, {s_G}') \right]
\end{align*}

Now consider applying to $M_G$' the state aggregation scheme, $\phi_m$, which satisfies the following:
\begin{align*}
\forall{a, s_G \in \mcS_G}  [&{\mcR_G}'(s1_G, a) = {\mcR_G}'(s2_G, a) \wedge \\
&{\mcT_G}'(s1_G, a, {s_G}') = {\mcT_G}'(s2_G, a, {s_G}') ]  \rightarrow \\
\phi_m(s1_G) = \phi_m(s2_G)
\end{align*}

$\phi_m$ is of the $\pM$ type and when applied to ${M_G}'$ results in $M_A$.

 \cite{li2006towards} demonstrate that abstraction schemes of the $\pM$ type maintain Q values so we know that $\forall{s_G \in \mcS} Q_{G'}(s_G) = Q_{A}(s_G)$.

Knowing that the Q values in $M_A$ are identical to those in ${M_G}'$, we now demonstrate that those of $M_G$ are boundedly close to those of ${M_G}'$ and then conclude by applying Lemma 1 (which states similar Q values in the abstract and ground MDP results in near optimal behavior of the optimal abstract policy applied to the ground MDP).
